---
title: "README"
author: "Bob Rudis"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

passivetotal is an R package to interface with the [PassiveTotal API](https://www.passivetotal.org/api/docs)

The following functions are implemented:

- `add_tag` :	Add a tag to a domain name or IP address
- `get_classification` :	Get classification for a domain or IP address
- `get_metadata` :	Get metadata about a domain or IP address
- `get_passive` :	Get dynamic status of domain
- `get_subdomains` :	Get subdomains for a domain
- `get_tags` :	Get user tags for a domain or IP address
- `get_unique` :	Get unique resolution information including frequency count
- `is_dynamic_associated` :	Get whether a domain is associated with a dynamic DNS provider
- `is_on_watchlist` :	Get watch status for a domain or IP address
- `is_sinkhole` :	Check sinkhole status of an IP address
- `passive_api_key` :	Get or set `PASSIVETOTAL_API_KEY` value
- `remove_tag` :	Remove a tag fgrom a domain name or IP address
- `set_classification` :	Set a classification for a domain or IP address
- `set_compromised` :	Set `ever_compromised` status for a domain or IP address
- `set_dynamic_associated` :	Set dynamic status of domain
- `set_sinkhole` :	Set sinkhole status of IP address
- `set_watching` :	Set watch status for a domain
- `was_ever_compromised` :	Get whether a site was ever compromised

### News

- Version 0.1.0 released
- Version 0.1.1 released : completed documentation; tested with `--as-cran` and fixed errors & warnings

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/passivetotal")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(passivetotal)

# current verison
packageVersion("passivetotal")

get_metadata("www.passivetotal.com")

get_passive("107.170.89.121")

```

### Test Results

```{r}
library(passivetotal)
library(testthat)

date()

test_dir("tests/")
```

