---
title: "README"
author: "Bob Rudis"
date: June 10, 2015
output:
  md_document:
    variant: markdown_github
---

passivetotal is an R package to interface with the [PassiveTotal API](https://www.passivetotal.org/api/docs)

The following functions are implemented:

- `add_tag` : function (domain_or_ip, tag)  
- `get_classification` : function (domain_or_ip)  
- `get_metadata` : function (domain_or_ip)  
- `get_passive` : function (domain_or_ip)  
- `get_subdomains` : function (domain)  
- `get_tags` : function (domain_or_ip)  
- `get_unique` : function (domain_or_ip)  
- `is_dynamic_associated` : function (domain)  
- `is_on_watchlist` : function (domain_or_ip)  
- `is_sinkhole` : function (ip)  
- `passive_api_key` : function (force = FALSE)  
- `remove_tag` : function (domain_or_ip, tag)  
- `set_classification` : function (domain_or_ip, classification)  
- `set_compromised` : function (domain_or_ip, is_compromised)  
- `set_dynamic_associated` : function (domain_or_ip, is_dynamic)  
- `set_sinkhole` : function (domain_or_ip, is_sinkhole)  
- `set_watching` : function (domain_or_ip, is_watching)  
- `was_ever_compromised` : function (domain_or_ip)

### News

- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/passivetotal")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(passivetotal)

# current verison
packageVersion("passivetotal")

get_metadata("www.passivetotal.com")

get_passive("107.170.89.121")

```

### Test Results

```{r}
library(passivetotal)
library(testthat)

date()

test_dir("tests/")
```

