---
output: rmarkdown::github_document
---

`passivetotal` is an R package to interface with the [PassiveTotal API](https://api.passivetotal.org/api/docs/)

This has BREAKNG CHANGES since it now only works with version 2 of the API.

You should set `PASSIVETOTAL_USER` & `PASSIVETOTAL_API_KEY` in `.Renviron` or you'll either be prompted for them or will need to pass them to each function manually.

NOTE that all the API functions are wrapped with `memoise::meomoise`, meaning that
they cache results. Use the `forget` function to clear the cache for any given
function.

The following functions are implemented:

- `account_history`: Get history associated with your account.
- `account_info`: Get account details your account.
- `account_notifications`: Get notifications that have been posted to your account.
- `account_organization`: Get details about the organization your account is associated with.
- `account_sources`: Get source details for a specific source.
- `account_teamstream`: Get the teamstream for the organization your account is associated with.
- `is_compromised`: Get the status of an observable
- `is_dynamic`: Get the status of an observable
- `is_fqdn`: Validate that a string looks like a fully qualified domain name
- `is_ipv4`: Validate that a string is an IPv4 address
- `is_monitored`: Get the status of an observable
- `is_sinkhole`: Get the status of an observable
- `passive_auth`: Get or set `PASSIVETOTAL_USER` & `PASSIVETOTAL_API_KEY` values
- `passive_classification`: Get the status of a classification domain
- `passive_dns`: Get passive DNS data
- `passive_enrich`: Enrich the given query with metadata
- `passive_host`: Get detailed information about a host
- `passive_malware`: Get malware data
- `passive_osint`: Get opensource intelligence data
- `passive_ssl_certificate`: Get the SSL certificate associated with the SHA-1.
- `passive_ssl_history`: Get the SSL certificate history associated with an IP address or SHA-1
- `passive_ssl_search`: Get the SSL certificate associated with the SHA-1.
- `passive_status`: Get the status of an observable
- `passive_subdomains`: Get subdomains using a wildcard query
- `passive_tags`: Get the tags for a query value
- `passive_tag_search`: Search for items based on tag value
- `passive_tracker`: Get all tracking codes for a domain or IP address.
- `passive_tracker_search`: Get hosts matching a specific tracker ID
- `passive_unique`: Get unique resolutions from passive DNS data
- `passive_whois`: Get WHOIS data for a domain or IP address
- `passive_whois_search`: Get WHOIS records based on field matching queries.

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/passivetotal")
```
```{r message=FALSE, eval=FALSE}
library(passivetotal)
library(dplyr)
library(jsonlite)

is_fqdn("rud.is") 
is_ipv4("10.10.10.10")

toJSON(passive_classification("passivetotal.org"), pretty=TRUE)

tbl_df(passive_dns("passivetotal.org")$results)
toJSON(passive_subdomains("*.passivetotal.org"), pretty=TRUE)
toJSON(passive_unique("passivetotal.org"), pretty=TRUE)

passive_host("passivetotal.org") 
passive_malware("xxxmobiletubez.com")
passive_osint("xxxmobiletubez.com") 
toJSON(passive_enrich("passivetotal.org"), pretty=TRUE)

toJSON(passive_ssl_certificate("e9a6647d6aba52dc47b3838c920c9ee59bad7034"), pretty=TRUE)
toJSON(passive_ssl_history("52.8.228.23"), pretty=TRUE)
toJSON(passive_ssl_search(query="www.passivetotal.org", field="subjectCommonName"), pretty=TRUE)

passive_status("passivetotal.org", "compromised")
passive_status("passivetotal.org", "dynamic")
passive_status("passivetotal.org", "monitor")
passive_status("52.8.228.23", "sinkhole")
passive_status("52.8.228.23", "s") 

passive_tracker_search(query="UA-61048133", type="GoogleAnalyticsAccountNumber") 
passive_tracker("passivetotal.org")

toJSON(passive_whois("passivetotal.org"), pretty=TRUE)
passive_whois_search(query="domains@riskiq.com", field="email") 
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
